On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2020-11-11 paper/cav_determinisim_main.tex
Added diagrams for variance description and plot for nice analysis

@@

@@

With the advent of more AI systems becoming adaptive, meaning that the system may change it's response to the same stimulus over time, the notion of repeatability will need reassessing in the context of verification. The main research question here is what will constitute `the same' which will be important for passing or failing verificatin tests but also for determining coverage.

>>>>

\begin{figure}[!t]
    \centering
    \begin{subfigure}{.48\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/Variance_predicition_tolerance_definition_diagram_a.pdf}
        \caption{}
        \label{variance_description_a}
    \end{subfigure}

    \begin{subfigure}{.48\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/Variance_predicition_tolerance_definition_diagram_b.pdf}
        \caption{}
        \label{variance_description_b}
    \end{subfigure}
    \caption{Demonstration of variance, precision, tolderance and determinism}
    \label{variance_description}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/NICE_analysis_summary.pdf}
    \caption{Summary of investigating the effect of NICE priority setting for 0\% and 75\% CPU \& GPU Resource Utilisation.}
    \label{NICEExperimentStressSummary}
\end{figure}

@@

With the advent of more AI systems becoming adaptive, meaning that the system may change it's response to the same stimulus over time, the notion of repeatability will need reassessing in the context of verification. The main research question here is what will constitute `the same' which will be important for passing or failing verification tests but also for determining coverage.
